### 2020-06-11 writeup/app_exp.tex
sec F

\textbf{Single-task based metric.}
We simplify the setup of this experiment by fixing the sample sizes of every task pair.
For sentiment analysis tasks, the source task uses xx training samples and the target task uses xx training samples for every task pair.
For image classification tasks, the training sample size is 10,000 for every task.

\textbf{Incremental training schedule.}

@@

\textbf{Theoretical validation.}

>>>>

\textbf{Single-task based metric.}
We simplify the setup of this experiment by fixing the sample sizes of every task pair.
For sentiment analysis tasks, the source task uses xx training samples and the target task uses $1000$ training samples for every task pair.
For image classification tasks, the training sample size is 10,000 for every task.

\textbf{Incremental training schedule.}
For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train} below to a round-robin training schedule baseline.
We set the parameters of Algorithm \ref{alg_inc_train} using batch size $32$ and epochs $T = xx$.
The threshold $\tau$ is set as the accuracy of the target task using the baseline training schedule.

For the case of six tasks,

@@

\textbf{Theoretical validation.}
For Figure \ref{fig_ab_sim}, \todo{how do we select each task pair?}
For Figure \ref{fig_ab_data} and Figure \ref{fig_ab_cov}, the sample size of the target task is fixed as $1000$.
We vary the sample size of the source task from $100$ to $3000$.
